The necessity of hypermedia RDF and an approach to achieve it

### 2012-04-12 eswc-2012/workshop2.tex
trim more tomorrow :)
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@224 43ef1190-90fd-4dd7-a769-d0121f02b80e

% TODO:
% Reformulate something on SPARQL about enabling
% More writing around factors?

@@

In the Linked Data Design
Issue\cite{linkeddataissue} Tim
Berners-Lee notes ``To make the data be effectively linked, someone
who only has the URI of something must be able to find their way the
SPARQL endpoint.'', but this is generally not possible today without
requiring out-of-band information.

>>>>

@@

In the \cite{linkeddataissue} Tim Berners-Lee
notes ``To make the data be effectively linked, someone who only has
the URI of something must be able to find their way the SPARQL
endpoint.'', but this is generally not possible today without
requiring out-of-band information.
